Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-01 tex/ClementiBarba2020.tex
Fix typo trecode -> treecode
Fix typo mode -> modes

Fix typo, repetion aa -> a

Fix typo given he -> given the

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with trecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some mode match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes. 
    Results in this paper were produced with strict reproducibility
    practices, and we share reproducibility packages for all, including
    input files, execution scripts, secondary data, post-processing code and
    plotting scripts, and the figures (deposited in Zenodo).
    In view of the many challenges faced, we propose that reproducible
    practices make replication and validation more feasible.

>>>>

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with treecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some modes match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes. 
    Results in this paper were produced with strict reproducibility
    practices, and we share reproducibility packages for all, including
    input files, execution scripts, secondary data, post-processing code and
    plotting scripts, and the figures (deposited in Zenodo).
    In view of the many challenges faced, we propose that reproducible
    practices make replication and validation more feasible.

### 2020-09-01 tex/discussion.tex
Fix typo trecode -> treecode
Fix typo mode -> modes

Fix typo, repetion aa -> a

Fix typo given he -> given the

Throughout all these activities aiming to replicate previous results and validate our computational model, we faced multiple challenges, starting with the complexity of the system under study. In both our source papers, we have systems that we were unable to fully 
model using \pygbe. For the case of Rockstuhl et al., even though they used a boundary element method, it was a 2D model instead of 3D like the one implemented in \pygbe. The computational work presented in Ellis et al.\ used a volumetric 
formulation (finite element method), whereas \pygbe implements a boundary integral one. Both works computed (or measured) quantities different from the extinction cross-section (computed in \pygbe), but given he relationship between their quantities (scattering cross-section and reflection)  
and ours (extinction cross section), via the wavelength (wavenumber) at which resonance happens, this was not a problem. To produce the end results for comparing against these works, however, we went through an 
exhaustive process of modeling, making assumptions, and even corrections. We were lacking any information regarding the solvers, discretization, meshes, etc., in the original papers. In the case of Ellis et al., we benefited from multiple communications with the authors, 
who made available the geometry and mesh of the pillar, as well as the dielectric data used as input for the simulations. Even though we appreciate this helpful interaction, replication studies should ideally not depend on communications with the original authors. 
In both cases, the secondary data presented in their results were not publicly available and we relied on a manually digitized version, obtained from the plots. This work is tedious and introduces uncertainties that would be avoided by releasing 
the secondary data.

>>>>

Throughout all these activities aiming to replicate previous results and validate our computational model, we faced multiple challenges, starting with the complexity of the system under study. In both our source papers, we have systems that we were unable to fully 
model using \pygbe. For the case of Rockstuhl et al., even though they used a boundary element method, it was a 2D model instead of 3D like the one implemented in \pygbe. The computational work presented in Ellis et al.\ used a volumetric 
formulation (finite element method), whereas \pygbe implements a boundary integral one. Both works computed (or measured) quantities different from the extinction cross-section (computed in \pygbe), but given the relationship between their quantities (scattering cross-section and reflection)  
and ours (extinction cross section), via the wavelength (wavenumber) at which resonance happens, this was not a problem. To produce the end results for comparing against these works, however, we went through an 
exhaustive process of modeling, making assumptions, and even corrections. We were lacking any information regarding the solvers, discretization, meshes, etc., in the original papers. In the case of Ellis et al., we benefited from multiple communications with the authors, 
who made available the geometry and mesh of the pillar, as well as the dielectric data used as input for the simulations. Even though we appreciate this helpful interaction, replication studies should ideally not depend on communications with the original authors. 
In both cases, the secondary data presented in their results were not publicly available and we relied on a manually digitized version, obtained from the plots. This work is tedious and introduces uncertainties that would be avoided by releasing 
the secondary data.

### 2020-09-01 tex/results.tex
Fix typo trecode -> treecode
Fix typo mode -> modes

Fix typo, repetion aa -> a

Fix typo given he -> given the

\paragraph{Dielectric data:} The study uses 6H-SiC as material, and the authors obtained their data from a a source that we
were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
via private communications from the authors of Ellis et al.\cite{ellis2016}.

>>>>

\paragraph{Dielectric data:} The study uses 6H-SiC as material, and the authors obtained their data from a source that we
were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
via private communications from the authors of Ellis et al.\cite{ellis2016}.
